{\it Proposal:}\\ Ultrashort pulsed microwave viral envelope disruption as a COVID-19 treatment

### 2020-10-05 documents/distribution.tex
Words
Propagation

\begin{center}
	{\bf \cite{Microwave2009} already mention this inhomogeneity; \cite{Elastic} perform a much better analysis than we do.}
\end{center}

@@

Inputting this yield stress distribution produces an inactivation field distribution that is far higher than that of \cite{Efficient2015}'s experimental data by some 200 V/m.

Let us therefore re-examine the microwave spectrum. Much of this data was found in order to try to simulate the inactivation mechanism by molecular dynamics, so it was not a complete waste of time.

@@

"95%.".

@@

This problem has a long history, stretching back to Cole-Cole's landmark 1942\cite{Dispersion1941} paper and \cite{Electrical1941}. Such concerning statements as 'mathematically ill-posed' are bandied about; however, standard optimization techniques work fine.

@@

Within a sample of a single species, there is $\approx$ 12.7\%  ($109 \pm 16.65 \text{ nm}$\cite{lauffer1944biophysical}, $115 \pm 12 \text{ nm}$ \cite{Characterization1984}) variation in diameter and  \cite{Characterization1984} variation in mass.

@@

Charge can be determined by the primary structure sequence. A table of net charges of Inf. A, and T4. however, a few influzena proteins have been found to have anomalous secondary structure charge.

>>>>

\begin{center}
	{\bf \cite{Microwave2009} already mention this inhomogeneity; \cite{Elastic} probably perform a much better analysis than we do.}
\end{center}

@@

Inputting this AFM-determined yield stress distribution produces an inactivation field distribution that is far higher than that of \cite{Efficient2015}'s experimental data by some 200 V/m.

This is not very surprising. Many reasonable assumptions are made that could account for this discrepancy; the homogeneous-sphere core-shell assumption, for instance.

However, it may be useful to re-examine the microwave spectrum with an eye towards the distribution.

\begin{toolchain}
Much of this data was found in order to try to simulate the inactivation mechanism by molecular dynamics, so it was not a complete waste of time.
\end{toolchain}

@@

@@

This problem has a long history, stretching back to Cole-Cole's landmark 1942\cite{Dispersion1941} paper:

@@

and \cite{Electrical1941}. Such concerning statements as 'mathematically ill-posed' are bandied about; however, standard stochastic fitting techniques work fine.

Within a sample of a single species of Inf. A, there is $\approx$ 12.7\%  ($109 \pm 16.65 \text{ nm}$\cite{lauffer1944biophysical}, $115 \pm 12 \text{ nm}$ \cite{Characterization1984}) variation in diameter and  \cite{Characterization1984} variation in mass.

@@

Charge can be determined by the primary structure sequence. A table of net charges of Inf. A, SARS, and T4 proteins is in the github. However, a few influzena proteins have been found to have anomalous secondary structure charge.

TODO: verify charge is $10^7$ e as found by Yang
